Fluid-mechanical erosion creates anisotropic porous media

### 2022-05-08 docs/PhysicsPaper/StokesErosion.tex
NM

%\documentclass[3p]{elsarticle}

% APS journals: PRL and PRF
% Note: All AIP and APS journals use the revtex package; both PRL and PRF are APS.
\documentclass[preprint, superscriptaddress, notitlepage]{revtex4-1}

@@

\author{Nicholas J.~Moore}
\affiliation{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
\author{Bryan D.~Quaife}
\affiliation{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
\author{Shang-Huan Chiu}
\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure*}[] %\centering
        \subfigure[ Vorticity field]{ \label{FigVort}
            \includegraphics[width=0.9 \textwidth]{figs/80circ8vort.pdf} } \\
        \subfigure[ Velocity magnitude]{ \label{FigVel}
            \includegraphics[width=0.9 \textwidth]{figs/80circ8vel.pdf} }
   \caption{80 eroding bodies}
   \label{FigVortVel}
\end{figure*}
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Data from 80circ8

@@

>>>>

\documentclass[3p]{elsarticle}

% APS journals: PRL and PRF
% Note: All AIP and APS journals use the revtex package; both PRL and PRF are APS.
%\documentclass[preprint, superscriptaddress, notitlepage]{revtex4-1}

% Physica D is elsevier 
%\documentclass[review]{elsarticle}

@@

\author{Nicholas J.~Moore}
%\affiliation{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
\author{Bryan D.~Quaife}
%\affiliation{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
\author{Shang-Huan Chiu}
%\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure*}[] \centering
        \subfigure[ Vorticity field]{ \label{FigVort}
            \includegraphics[width=0.9 \textwidth]{figs/80circ8vort.pdf} } \\
        \subfigure[ Velocity magnitude]{ \label{FigVel}
            \includegraphics[width=0.9 \textwidth]{figs/80circ8vel.pdf} }
   \caption{80 eroding bodies}
   \label{FigVortVel}
\end{figure*}
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Data from 80circ8

@@

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{}
\includegraphics[width = 0.99 \textwidth]{./figs/figA.pdf}
\caption{caption}
\end{figure*}
%---------------------------------------------------------%
